Growth model analysis

### 2018-02-08 manuscriptAnalysis/MS_Analysis.Rmd
changed lengthDATA to observedLength to get units correct for predictions

```{r}
library(arrayhelpers)
library(tidyverse)

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1517338587_bkt1997_Nimble.RData")
mcmc[['bkt']] <- mcmcProcessed
d <- dddG[[1]]

load("D:/projects/linkedModels/data/out/dG_1517344974_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1517347750_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

rm(dddG,ddG,dG,mcmcProcessed)

```{r custom theme}
theme_publication <- function(base_size=14, base_family="") {
  library(grid)
  library(ggthemes)
  (theme_foundation(base_size=base_size, base_family=base_family)
    + theme(plot.title = element_text(face = "bold",
                                      size = rel(1.2), hjust = 0.5),
            text = element_text(),
            panel.background = element_rect(colour = NA),
            plot.background = element_rect(colour = NA),
            axis.title = element_text(face = "bold",size = rel(1)),
            axis.title.y = element_text(angle=90,vjust =2),
            axis.title.x = element_text(vjust = -0.2),
            axis.text = element_text(),
            axis.line = element_line(colour="black"),
            axis.ticks = element_line(),
            panel.grid.major = element_line(colour="#f0f0f0"),
            panel.grid.minor = element_blank(),
            legend.key = element_rect(colour = NA),
            legend.position = "bottom",
            legend.direction = "horizontal",
            legend.key.size= unit(0.2, "cm"),
            legend.margin = unit(0, "cm"),
            legend.title = element_text(face="italic"),
            plot.margin=unit(c(10,5,5,5),"mm"),
            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
            strip.text = element_text(face="bold"),
            panel.border = element_rect(colour = "black")
    ))

@@

@@

# all three species
ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook'), aes(season, meanGr, color = species) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()+
  facet_wrap(~isYOY)

@@

@@

@@

```
```{r ind RE among spp}

@@

>>>>

```{r functions}
theme_publication <- function(base_size=14, base_family="") {
  library(grid)
  library(ggthemes)
  (theme_foundation(base_size=base_size, base_family=base_family)
    + theme(plot.title = element_text(face = "bold",
                                      size = rel(1.2), hjust = 0.5),
            text = element_text(),
            panel.background = element_rect(colour = NA),
            plot.background = element_rect(colour = NA),
            axis.title = element_text(face = "bold",size = rel(1)),
            axis.title.y = element_text(angle=90,vjust =2),
            axis.title.x = element_text(vjust = -0.2),
            axis.text = element_text(),
            axis.line = element_line(colour="black"),
            axis.ticks = element_line(),
            panel.grid.major = element_line(colour="#f0f0f0"),
            panel.grid.minor = element_blank(),
            legend.key = element_rect(colour = NA),
            legend.position = "bottom",
            legend.direction = "horizontal",
            legend.key.size= unit(0.2, "cm"),
            legend.margin = unit(0, "cm"),
            legend.title = element_text(face="italic"),
            plot.margin=unit(c(10,5,5,5),"mm"),
            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
            strip.text = element_text(face="bold"),
            panel.border = element_rect(colour = "black")
    ))

@@

```{r message=FALSE}
library(arrayhelpers)
library(tidyverse)

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1517846073_bkt1997_Nimble.RData")

# input data
d1 <- ddG[[1]][[1]]
d2 <- ddG[[1]][[2]]
meanSampleIntervalMean <- data.frame( meanSampleInterval = colMeans(d1$sampleIntervalMean), season = 1:d1$nSeasons )

#RECALCULATE gr for dataset. Filtering by maxSampleInterval in the creat ddddG step leaves in trailing lengths from the long samp intervals
d2 <- d2 %>%
  group_by(tag) %>%
  # arrange(tag,sampleNumber) %>%
  mutate( lagObservedWeight = lead(observedWeight),
          lagObservedLength = lead(observedLength),
          grWeight = exp(lagObservedWeight - observedWeight)/as.numeric((lagDetectionDate - detectionDate)),
          grLength = (lagObservedLength - observedLength)/as.numeric((lagDetectionDate - detectionDate))
  )  
#d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)

# output data
mcmc[['bkt']] <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1517850064_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1517853143_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

rm(ddG,dG,mcmcProcessed)

@@

# all three species
ggplot( cdMeansByisYOY %>% filter(riverOrdered == 'west brook', !(season == 2 & isYOY == 1)), aes(season, meanGr, color = species) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()+
  facet_wrap(~isYOY)

# all three species by river
ggplot( cdMeansByisYOY %>% filter(!(season == 2 & isYOY == 1)) , aes(season, meanGr, color = riverOrdered) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()+
  facet_grid(species~isYOY)

@@

```
```{r growth by movement}
d2$isYOY <- ifelse( d2$ageInSamples <= 3, 1, 2 )
d2 <-  d2 %>%
  group_by(tag) %>%
  mutate( lagRiverN = lead(riverN), 
          riverNMove = paste(riverN,lagRiverN, sep="_")
          #gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate)
          )

#d2 %>% filter(tag=='00088cbf44') %>% select(tag,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength)
table(d2$riverNMove)

cdMeansByisYOYriverNMove <- d2 %>%
  #mutate( gr = (observedLength - lagObservedLength)/as.integer(detectionDate - lagDetectionDate) ) %>%
  group_by(species,riverN,lagRiverN,season,isYOY) %>%
  summarize( meanGr = mean( grLength, na.rm = TRUE ),
             sdGr = sd( grLength, na.rm = TRUE ),
             n = n()) %>%
  mutate( meanGrUp = meanGr + sdGr,
          meanGrDn = meanGr - sdGr
          )

# 
ggplot( cdMeansByisYOYriverNMove %>% filter(!(season == 2 & isYOY == 1), species == "bkt", isYOY == 2) , aes(season, meanGr, color = factor(lagRiverN)) ) +
  geom_errorbar(aes(ymin = meanGrDn, ymax = meanGrUp), width = 0.25, position = pd) +
  geom_point( size = 2 ) +
  geom_line()+
  facet_wrap(~riverN)

d2 %>% filter(riverN == 1 & lagRiverN == 4) %>% select(tag,river,sampleNumber)
d2 %>% filter(riverN == 2, is.na(lagRiverN), !is.na(grLength)) %>% select(tag,riverN,sampleNumber,lagRiverN,observedLength,lagObservedLength,gr,grLength)
d2 %>% filter(tag=='00088cc059') %>% select(tag,riverOrdered,riverN,lagRiverN,sampleNumber,observedLength,lagObservedLength,gr,grLength)
```

@@

# as range plot
probs <- c(0.05,0.1,0.5,0.9,0.95)
q <- grInt[['bkt']] %>%
  group_by(isYOY,season,river) %>%
  summarize(
    p = list(probs),
    q = list(quantile(int,probs))
  ) %>%
  unnest() %>%
  spread(key = p, value = q)

p <- array2df(mcmc[['bkt']]$mean$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int") %>%
  mutate( season = as.numeric(season) ) %>%
  left_join(.,meanSampleIntervalMean, by = 'season')
p$intByDay <- p$int/p$meanSampleInterval
p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
p$parameter <- paste(p$river,p$season,sep="_")

pUp <- array2df(mcmc[['bkt']]$q97.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intUp") %>%
  mutate( season = as.numeric(season) ) 
pDown <- array2df(mcmc[['bkt']]$q2.5$grInt, levels = list(isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="intDown") %>%
  mutate( season = as.numeric(season) )
p$intByDayUp <- p$intUp/p$meanSampleInterval; p$intByDayDown <- p$intDown/p$meanSampleInterval
p$intByDay <- ifelse(p$isYOY == 1 & p$season == 2, NA, p$intByDay)
p <- left_join(p,pUp) %>% left_join(.,pDown)

   ggplot(p, aes(x = intByDay, y = reorder(parameter,intByDay,na.rm=TRUE), color = factor(season), shape = factor(season))) + 
      geom_point(size = 3) +
      facet_grid(~isYOY)

      geom_segment(aes(x = Low, 
      xend = High, yend = reorder(Parameter, median)), 
      size = 1.5) + geom_segment(aes(x = low, xend = high, 
      yend = reorder(Parameter, median)), size = 0.5) + 
      xlab("HPD") + ylab("Parameter")

```{r}

@@

```{r ind RE among spp}

@@

```{r tables}

round(mcmc$summary$all.chains[startsWith(attributes(mcmc$summary$all.chains)$dimnames[[1]], "grBeta["),],2)
